Time-resolved optical conductivity and Higgs oscillations\\in two-band dirty superconductors

### 2020-10-31 paper/paper_v1.tex
a
standard commit

\documentclass[aps,prb,reprint,noeprint,superscriptaddress]{revtex4-2}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{braket}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{comment}
\usepackage{siunitx}
\usepackage{float}
\usepackage[
    pdftitle={},
    pdfauthor={},
    colorlinks=true,
    unicode=true,
    pdfborder={0 0 0},
    allcolors=blue
]{hyperref}

@@

\author{Rafael Haenel}
\affiliation{Max Planck Institute for Solid State Research,
70569 Stuttgart, Germany}
\affiliation{Quantum Matter Institute, University of British Columbia, Vancouver V6T 1Z4, Canada}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\columnwidth]{figures/fig3.pdf}
	\caption{(A,B) Conductivity spectra for sweeped pump-probe delay $\delta
	t_{\text{p-p}}$ to third order in $A$. (C) False-color plot of
$\sigma' $ which was average-subtracted and normalized to show the oscillations.
A phase shift occurs across the resonance at $2\Delta_{\text{eq}}$ of the quench pulse
frequency. (D) Fourier spectrum of panel (C) showing that frequency of
conductivity oscillation is peaked at $2\Delta_{\text{eq}}$.}
\end{figure}
%\begin{comment}
\section{Multi-band superconductivity}
\label{sec:multiband}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Higgs oscillations}
\label{sec:higgs_oscillations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/two_band_cond.png}
    \caption{\label{fig:two_band_cond}%
    Equilibrium optical conductivity of a two-band superconductor with gaps in different impurity scattering limits (clean-clean case rescaled as response is much smaller?)}
\end{figure}%

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/gap_osci.png}
    \caption{\label{fig:gap_osci}%
    Higgs oscillations excited by a pump pulse with enough bandwidth to cover both gaps for the different impurity scattering limits shown in Fig.~\ref{fig:two_band_cond}}
\end{figure}%

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/noneq_cond.png}
    \caption{\label{fig:noneq_cond}%
    Nonequilibrium optical conductivity of a pump-probe experiment for the different impurity scattering limits shown in Fig.~\ref{fig:two_band_cond}}
\end{figure}%

@@

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/leggett_oscillations.png}
    \caption{\label{fig:leggett_oscillations}%
    Induced amplitude (Higgs) and out-of-phase (Leggett) oscillations of a two-band superconductor for different impurity scattering rates}
\end{figure}%

@@

Leggett mode has been potentially measured in between the two gaps. Discuss this
and also refer to Schnyder Nature Comm. Figure out the parameter regime that
inverted the gaps. Reproduce (or see what was wrong) with Murotani who also
choose parameters such that the Leggett mode is inside the gap.

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/leggett_coupling.png}
    \caption{\label{fig:leggett_coupling}%
    Frequency of Leggett mode as function of interband coupling strength in the dirty limit}
\end{figure}%

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/influence_pump_pulse_freq.png}
    \caption{\label{fig:influence_pump_pulse_freq}%
    Influence of pump pulse frequency}
\end{figure}%

>>>>

\documentclass[aps,prb,reprint,noeprint,superscriptaddress]{revtex4-1}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{braket}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{comment}
\usepackage{siunitx}
\usepackage{float}
\usepackage[
    pdftitle={},
    pdfauthor={},
    colorlinks=true,
    unicode=true,
    pdfborder={0 0 0},
    allcolors=blue
]{hyperref}

@@

\author{Rafael Haenel2}
\affiliation{Max Planck Institute for Solid State Research,
70569 Stuttgart, Germany}
\affiliation{Quantum Matter Institute, University of British Columbia, Vancouver V6T 1Z4, Canada}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\columnwidth]{figures/fig3.pdf}
	\caption{(A,B) Conductivity spectra for sweeped pump-probe delay $\delta
	t_{\text{p-p}}$ to third order in $A$. (C) False-color plot of
$\sigma' $ which was average-subtracted and normalized to show the oscillations.
A phase shift occurs across the resonance at $2\Delta_{\text{eq}}$ of the quench pulse
frequency. (D) Fourier spectrum of panel (C) showing that frequency of
conductivity oscillation is peaked at $2\Delta_{\text{eq}}$.}
\end{figure}
%\begin{comment}
\section{Multi-band superconductivity}
\label{sec:multiband}

\begin{figure}[ht]
	\centering
	\includegraphics[width=\columnwidth]{figures/m-fig1.pdf}
	\caption{Real part $\sigma'$ (A,C) and imaginary part $\sigma''$ (B,D)
		of optical conductivities to first order in $A$ 
	for various impurity scattering rates at $T=\SI{4}{\kelvin}$ (A,B) and
various temperatures at $\gamma/2\Delta=10$. $\sigma'$ show a characteristic
conductivity gap below $T_C$ and both $\sigma'$, $\sigma''$ diverge in the
static limit.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Higgs oscillations}
\label{sec:higgs_oscillations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{figures/fig-cond-2d-fourcases}
  \caption{Caption}
\end{figure}
\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-three-pulses}
  \caption{Caption}
\end{figure*}

@@

@@

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{figures/fig-driving}
  \caption{Caption}
\end{figure}
\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{figures/2_a}
  \includegraphics[width=\columnwidth]{figures/2_b}
\end{figure}

@@

@@

Leggett mode has been potentially measured in between the two gaps. Discuss this
and also refer to Schnyder Nature Comm.

@@
